---
title: "Stats 506, F20, Final Project"
author: "Yanyu Long, longyyu@umich.edu"
date: "December 07, 2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
---

```{css, include = TRUE, echo = FALSE}
body{ /* Normal */
  font-size: 15px;
}
td{ /* Table  */
  font-size: 14px;
}
#TOC{ /* Table of contents */
  font-size: 16px;
}
span.math{ /* Formulas */
  font-size: 13px;
}
h2{ /* Header 2 */
  font-size: 28px;
}
h3{ /* Header 3 */
  font-size: 22px;
}
h4:not([class]){ /* Header 4 */
  font-size: 18px;
  text-decoration: underline;
}
h5{ /* Header 5 */
  font-size: 15px;
  font-weight: bold;
}
blockquote {
  font-size: 14px;
}
pre { /* Scrollable code block */
  max-height: 300px;
  overflow-y: auto;
}
.fn { /* File names */
  color: IndianRed;
}
.narrow { /* Narrow tables */
  width: 40%;
  margin: auto; 
}
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  include = TRUE, 
  echo = FALSE,
  warning = FALSE, 
  message = FALSE,
  comment = "",
  fig.align = "center"
)
source("final_project.R")
```

## To-do items

*  Introduction: add why the question is interesting
*  Conclusion: add analysis
*  Vertical-align the result table's NA values

## Introduction

This report attempts to answer the question:  

> How does the choice of wall construction materials evolve over time? Are the trends different across census divisions?  
  
To answer these questions, I first compute the proportion of wall construction material types by year of construction to analyze the overall trend. 
Then, I further divide the data by census division to see if different regions show distinct patterns.  


## Data / Methods

This project uses the 2012 US Commercial Building Energy Consumption Survey (CBECS) published by the U.S. Energy Information Administration (EIA): 

*  2012 CBECS survey microdata ([2012_public_use_data_aug2016.csv]{.fn})
*  Variable and response codebook ([2012microdata_codebook.xlsx]{.fn})

*&ast; Data* are downloaded from [the EIA's website](https://www.eia.gov/consumption/residential/data/2009/index.php) using the shell script `download_data.sh`, which can be found in the project's repository. 


!Describe the methods you used. There should be enough detail here that I could repeat your analysis. Focus on what you did, not how you did it. 


The data files and source code can be found in [this GitHub repository](https://github.com/longyyu/Stats506_FinalProj).

## Results {.tabset .tabset-pills}

### Figure

```{r est_yr_plot, fig.width = 8, fig.height = 8, fig.cap = "**Fig 1.** % of wall material types by year of construction"}
print(pic_yr)
```

<br>

```{r est_yr_region_plot, fig.width = 10, fig.height = 12, fig.cap = "**Fig 2.** % of wall material types by year of construction and census region"}
print(pic_yr_region)
```

### Table

```{r est_yr_region_table}
html_table
```

## {- .unlisted .unnumbered}


## Conclusion

!What do your results allow us to conclude about the question you posed? What are the strengths and limitations of your analysis?

*  Overall, central air conditioning systems are the most popular options 
for US households, followed by individual window/wall or portable units. 
*  Households in very cold/cold area show stronger preferences for individual 
units than other climate zones. 
*  Urban/rural type does not have a significant influence on the 
preferences. 
*  The differences between 2009 and 2015 results did not present an obvious 
pattern. However, it is worth noting that the `not applicable` rate in the 
marine climate zone dropped from over 60% in 2009 to around 47% in 2015. 
This may indicate that more households in the marine area started to use AC 
equipment. But it can also be caused by other factors such as survey design. 


